Ellipsoids (v1.0): 3D Magnetic modelling of ellipsoidal bodies

### 2017-06-08 manuscript/manuscript.tex
include a section about the ambiguity between confocal ellipsoids

%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for copernicus.cls
%% The class file and some style files are bundled in the Copernicus Latex Package which can be downloaded from the different journal webpages.
%% For further assistance please contact the Copernicus Publications at: publications@copernicus.org
%% http://publications.copernicus.org

@@

Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}^{\dagger}$
(Eq. \ref{eq:Hi-tilde}) by the transformed
susceptibility tensor $\tilde{\mathbf{K}}$
(Eq. \ref{eq:H-tilde}) to obtain
\begin{equation}
\begin{split}
\tilde{\mathbf{M}}
&= \tilde{\mathbf{K}}
\left( \mathbf{I} + \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \\
&=
\left( \mathbf{I} + \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
\end{split} \: ,
\label{eq:M-tilde}
\end{equation}
where $\tilde{\mathbf{M}}$
represents the transformed magnetization, as can be easily
verified by using Eqs. \ref{eq:M-KH} and \ref{eq:H-tilde}.
The matrix identity used for obtaining the second line of Eq.
\ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
Equation \ref{eq:M-tilde} can be easily generalized for the case in
which the ellipsoid has also a uniform remanent magnetization
$\tilde{\mathbf{M}}_{R}$. Let us first consider that
the uniform remanent magnetization satisfies the condition
$\tilde{\mathbf{H}}_{A} = \tilde{\mathbf{K}}^{-1} \tilde{\mathbf{M}}_{R}$,
where $\tilde{\mathbf{H}}_{A}$ represents a hypothetical
uniform ancient field. Then, if we assume that $\tilde{\mathbf{H}}_{0}$,
in Eqs. \ref{eq:Hi-tilde} and \ref{eq:M-tilde},
is in fact the sum of the inducing magnetic field $\tilde{\mathbf{H}}_{0}$
and the hypothetical ancient field $\tilde{\mathbf{H}}_{A}$, we obtain the
following generalized equation
\begin{equation}
\mathbf{M} = \mathbf{\Lambda}
\left(\mathbf{K} \, \mathbf{H}_{0} + \mathbf{M}_{R} \right) \: ,
\label{eq:M-remanence}
\end{equation}
where
\begin{equation}
\mathbf{\Lambda} = \mathbf{V}
\left( \mathbf{I} + \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\mathbf{V}^{\top} \: .
\label{eq:Lambda}
\end{equation}
Despite of the coordinate system transformation represented by the
matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
Eq. \ref{eq:M-remanence} is consistent with that given by
\citet[Eq. ~38]{clark1986}. It shows the combined effect of the
anisotropy of magnetic susceptibility (AMS) and the shape anisotropy.
The AMS is represented by the susceptibility tensor $\mathbf{K}$
(Eq. \ref{eq:K}) and reflects the
preferred orientation of the magnetic minerals forming the
body. The susceptibility tensor appears in Eq. \ref{eq:M-remanence},
defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a),
and Eq. \ref{eq:Lambda}, defined in the local coordinate system
(Fig. \ref{fig:orientation-angles}b).
The shape anisotropy is represented, in Eq. \ref{eq:M-remanence}, by the
depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$ and
reflects the self-demagnetization associated to the body shape.
Notice that the resultant magnetization $\mathbf{M}$
(Eq. \ref{eq:M-remanence}) does not necessarily have
the same direction as the inducing field $\mathbf{H}_{0}$
(Eq. \ref{eq:H0}).
The angular difference between the resultant magnetization
and the inducing field depends on the combined effect of the
anisotropy of magnetic susceptibility and the shape anisotropy.

@@

>>>>

% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for copernicus.cls
%% The class file and some style files are bundled in the Copernicus Latex Package which can be downloaded from the different journal webpages.
%% For further assistance please contact the Copernicus Publications at: publications@copernicus.org
%% http://publications.copernicus.org

@@

Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}^{\dagger}$
(Eq. \ref{eq:Hi-tilde}) by the transformed
susceptibility tensor $\tilde{\mathbf{K}}$
(Eq. \ref{eq:H-tilde}) to obtain
\begin{equation}
\begin{split}
\tilde{\mathbf{M}}
&= \tilde{\mathbf{K}}
\left( \mathbf{I} + \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \\
&=
\left( \mathbf{I} + \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
\end{split} \: ,
\label{eq:M-tilde}
\end{equation}
where $\tilde{\mathbf{M}}$
represents the transformed magnetization, as can be easily
verified by using Eqs. \ref{eq:M-KH} and \ref{eq:H-tilde}.
The matrix identity used for obtaining the second line of Eq.
\ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.

Equation \ref{eq:M-tilde} can be easily generalized for the case in
which the ellipsoid has also a uniform remanent magnetization
$\tilde{\mathbf{M}}_{R}$. Let us first consider that
the uniform remanent magnetization satisfies the condition
$\tilde{\mathbf{H}}_{A} = \tilde{\mathbf{K}}^{-1} \tilde{\mathbf{M}}_{R}$,
where $\tilde{\mathbf{H}}_{A}$ represents a hypothetical
uniform ancient field. Then, if we assume that $\tilde{\mathbf{H}}_{0}$,
in Eqs. \ref{eq:Hi-tilde} and \ref{eq:M-tilde},
is in fact the sum of the inducing magnetic field $\tilde{\mathbf{H}}_{0}$
and the hypothetical ancient field $\tilde{\mathbf{H}}_{A}$, we obtain the
following generalized equation
\begin{equation}
\mathbf{M} = \mathbf{\Lambda}
\left(\mathbf{K} \, \mathbf{H}_{0} + \mathbf{M}_{R} \right) \: ,
\label{eq:M-remanence}
\end{equation}
where
\begin{equation}
\mathbf{\Lambda} = \mathbf{V}
\left( \mathbf{I} + \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\mathbf{V}^{\top} \: .
\label{eq:Lambda}
\end{equation}
Despite of the coordinate system transformation represented by the
matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
Eq. \ref{eq:M-remanence} is consistent with that given by
\citet[Eq. ~38]{clark1986}. It shows the combined effect of the
anisotropy of magnetic susceptibility (AMS) and the shape anisotropy.
The AMS is represented by the susceptibility tensor $\mathbf{K}$
(Eq. \ref{eq:K}) and reflects the
preferred orientation of the magnetic minerals forming the
body. The susceptibility tensor appears in Eq. \ref{eq:M-remanence},
defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a),
and Eq. \ref{eq:Lambda}, defined in the local coordinate system
(Fig. \ref{fig:orientation-angles}b).
The shape anisotropy is represented, in Eq. \ref{eq:M-remanence}, by the
depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$ and
reflects the self-demagnetization associated to the body shape.
Notice that the resultant magnetization $\mathbf{M}$
(Eq. \ref{eq:M-remanence}) does not necessarily have
the same direction as the inducing field $\mathbf{H}_{0}$
(Eq. \ref{eq:H0}).
The angular difference between the resultant magnetization
and the inducing field depends on the combined effect of the
anisotropy of magnetic susceptibility and the shape anisotropy.

@@

\subsubsection{Ambiguity between confocal ellipsoids with the same magnetic moment}

There is a fundamental non-uniqueness of ellipsoidal bodies, analogous to the
equivalence of concentric spheres with the same magnetic moment.
To show this ambiguity, let us first
consider an ellipsoid which is immersed in a uniform inducing
field and has semi-axes $a$, $b$, and $c$, isotropic susceptibility $\chi$
and no remanence.
The magnetization of this ellipsoid, defined in the local coordinate system,
can be obtained by using Eqs. \ref{eq:K-isotropic}, \ref{eq:H-tilde}, and \ref{eq:M-tilde}
as follows:
\begin{equation}
\tilde{\mathbf{M}} = \chi \left( \mathbf{I} + \chi \, \tilde{\mathbf{N}}^{\dagger} 
\right)^{-1} \tilde{\mathbf{H}}_{0} \: .
\label{eq:M-tilde-K-isotropic}
\end{equation}
In this case, the magnetic moment $\tilde{\mathbf{P}}$, defined in the
local coordinate system, is given by
\begin{equation}
\tilde{\mathbf{P}} = \vartheta \tilde{\mathbf{M}} \: ,
\label{eq:P-tilde}
\end{equation}
where $\vartheta = \frac{4}{3}\pi a b c$ is the ellipsoid volume.
From Eqs. \ref{eq:M-tilde-K-isotropic} and \ref{eq:P-tilde},
we can easily show that, if the inducing field $\tilde{\mathbf{H}}_{0}$
is parallel to a semi-axis $e_{i}$, where $i = 1, 2, 3$, $e_{1} = a$, $e_{2} = b$,
$e_{3} = c$, only the $i$th component $P_{i}$ of the magnetic moment $\tilde{\mathbf{P}}$
is non null and given by
\begin{equation}
P_{i} = \vartheta \frac{\chi \, H_{0}}{1 + \chi \, \tilde{n}^{\dagger}_{ii}} \: ,
\label{eq:P-tilde-i}
\end{equation}
where $H_{0}$ is the intensity of the inducing field $\tilde{\mathbf{H}}_{0}$
and the demagnetizing factor $\tilde{n}^{\dagger}_{ii}$ is defined
by Eq. \ref{eq:n-tilde-dagger-11-triaxial}, \ref{eq:n-tilde-dagger-11-prolate},
or \ref{eq:n-tilde-dagger-11-oblate}, according to the ellipsoid type.

Now, consider a confocal ellipsoid with semi-axes $a^{\prime} = \sqrt{a^2+u}$,
$b^{\prime} = \sqrt{b^2+u}$, and $c^{\prime} = \sqrt{c^2+u}$, where $u$ is a
positive real number. From Eq. \ref{eq:P-tilde-i}, we can define the
isotropic susceptibility $\chi^{\prime}$ that is necessary to this confocal
ellipsoid produce the same magnetic moment $\tilde{\mathbf{P}}$ (Eq. \ref{eq:P-tilde})
as follows:
\begin{equation}
\chi^{\prime} = \frac{P_{i}}{\vartheta^{\prime} \, H_{0} - \tilde{n}^{\dagger}_{ii} \, P_{i}} \: ,
\label{eq:chi-prime}
\end{equation}
where $\vartheta^{\prime} = \frac{4}{3}\pi a^{\prime} b^{\prime} c^{\prime}$ and
$\tilde{n}^{\dagger}_{ii}$ is the new demagnetizing factor computed for the
confocal ellipsoid by using Eq. \ref{eq:n-tilde-dagger-11-triaxial}, \ref{eq:n-tilde-dagger-11-prolate},
or \ref{eq:n-tilde-dagger-11-oblate}, according to the ellipsoid type.
It can be shown that this confocal ellipsoid produce the same magnetic field
as the ellipsoid with semi-axes $a$, $b$, and $c$.

This ambiguity between confocal ellipsoids with the same magnetic moment
has already been pointed out by Clark (2014) and is verified for the
particular case in which the uniform inducing field is parallel
to an ellipsoid axis.
Otherwise, the magnetic field produced by the confocal ellipsoids
will be different due to the shape anisotropy.
